\section{Add Administrator Rights To User}

% --Description--
%
\begin{cpart}{Description}
In case a new administrator needs to be assigned, when e.g. the current administrator  leaves the company, the administrator needs to give permissions to any of the users of the system.
\end{cpart}


% --Actors--
%
\begin{cpart}{Actors}
Administrator
\end{cpart}

% --Preconditions--
%
\begin{cpart}{Preconditions}
The administrator is logged in to the system and is currently on the administrator page.
\end{cpart}

% --Basic Flow--
%
\begin{cpartList}{Basic Flow}
  \item The administrator activates the administrator list and searches for a user.
  \item The system gives a list of users that match the search conditions.
  \item The administrator picks a user from the list.
  \item The system gives administrator privileges to the user.
  \item The system writes a log entry for the activity of the user with the current time and date.
  \item The system notifies the administrator of the change by displaying the user in the list of administrators.
\end{cpartList}

% --Exception Flows--
%
\begin{cpartList}{Exception Flows}
  \begin{innerList}{2}{a}{No user with the entered user information can be found.}
    \item Display error message.
    \item The use case is exited.
  \end{innerList}

  \begin{innerList}{4}{a}{The administrator does no longer have administrator privileges.}
    \item Display error message.
    \item Return to the main page.
  \end{innerList}
\end{cpartList}

% --Postconditions--
%
\begin{cpart}{Postconditions}
The user is added to the list of administrators and has administrator privileges.
\end{cpart}

\seq{addAdminRights}
