\section{Create Account}

% If you don't have any list items for the alternate
% flows or the exception flows, change cpartList to cpart
% and just emphasize that with \textit{none}.

% --Description--
%
\begin{cpart}{Description}
The administrator creates accounts for all users. When a new user should be created they give their information to the administrator, who then creates the account. The information a user needs to create an account is the email, desired user name and desired password of the user. The rules for user names and passwords have not yet been defined.
\end{cpart}


% --Actors--
%
\begin{cpart}{Actors}
User, Administrator
\end{cpart}

% --Preconditions--
%
\begin{cpart}{Preconditions}
The system is already setup and an administrator exists. The administrator is logged in to the system.
\end{cpart}

% --Basic Flow--
%
\begin{cpartList}{Basic Flow}
  \item The user requests an account and gives information to the administrator.
  \item The administrator accesses the user creation page.
  \item The administrator enters the users data and requests creation of the new account.
  \item The system saves the user data in the database.
\item The system writes a log entry for the activity of the user with the current time and date.
  \item The system notifies the administrator that the account has been created.
    \item The system writes a log entry for the activity of the user with the current time and date.
\end{cpartList}

% --Exception Flows--
%
\begin{cpartList}{Exception Flows}
  \begin{innerList}{4}{a}{A user with the entered user name or email address already exists.}
    \item The system notifies the administrator.
    \item The administrator asks the user for different user information.
    \item The administrator returns to step 3.
  \end{innerList}

  \begin{innerList}{4}{b}{One or more of the entered information do not comply with the rules.}
    \item The system notifies the administrator.
    \item The administrator asks the user for different user information.
    \item The administrator returns to step 3.
  \end{innerList}
\end{cpartList}

% --Postconditions--
%
\begin{cpart}{Postconditions}
A new user account with the users information has been created.
\end{cpart}

\clearpage
