\section{Deactivate Account}

% --Description--
%
\begin{cpart}{Description}
The administrator manages all user accounts including the deactivation of accounts. The administrator can find a user by putting in either the user name or the email address. A deactivated user will still show up in the statistics but is not able to log in to the system.
\end{cpart}


% --Actors--
%
\begin{cpart}{Actors}
Administrator
\end{cpart}

% --Preconditions--
%
\begin{cpart}{Preconditions}
The system is already setup and an administrator exists. The administrator is logged in to the system.
\end{cpart}

% --Basic Flow--
%
\begin{cpartList}{Basic Flow}
  \item The administrator searches for a user by putting in the users information.
  \item The system shows a list of users fitting the search criteria.
  \item The administrator chooses the user he wants to deactivate and requests deactivation.
  \item The system asks for confirmation.
  \item The administrator confirms.
  \item The system notifies the administrator of the deactivation of the users account.
    \item The system writes a log entry for the activity of the user with the current time and date.
\end{cpartList}

% --Exception Flows--
%
\begin{cpartList}{Exception Flows}
  \begin{innerList}{4}{a}{Alternate flow.}
    \item The system notifies the administrator.
    \item The use case is exited.
  \end{innerList}

  \begin{innerList}{4}{b}{Alternate flow.}
    \item The system notifies the administrator that an administrator cannot deactivate him-/herself.
    \item The administrator is routed back to the administrator page.
  \end{innerList}
\end{cpartList}

% --Postconditions--
%
\begin{cpart}{Postconditions}
The user account has been deactivated.
\end{cpart}

\clearpage
