\section{Geofence Settings: Disable On Server}

% --Description--
%
\begin{cpart}{Description}
The server should be able to ignore automatic geofence state-switch requests from smartphones.
\end{cpart}


% --Actors--
%
\begin{cpart}{Actors}
Administrator
\end{cpart}

% --Preconditions--
%
\begin{cpartList}{Preconditions}
\item The server is up.
\item The geofence functionality is enabled in the server.
\item The administrator is logged in and is in the view where the geofence switch is located.
\end{cpartList}

% --Basic Flow--
%
\begin{cpartList}{Basic Flow}
  \item The administrator clicks on the enable/disable switch to disable the functionality.
  \item The system disables the geofence functionality.
  \item The system notifies the administrator that geofence functionality is disabled.
\end{cpartList}

% --Alternate Flows--
%
\begin{cpartList}{Alternate Flows}
  \begin{innerList}{1}{a}{The functionality is already disabled.}
    \item The system enables the geofence functionality.
    \item The system notifies the user that the geofence functionality is enabled.
  \end{innerList}
\end{cpartList}

% --Exception Flows--
%
\begin{cpartList}{Exception Flows}
  \begin{innerList}{1}{a}{The administrator has lost its elevated rights.}
    \item The system notifies the former administrator about the missing rights.
    \item The system notifies the user that the state-switch failed.
  \end{innerList}
\end{cpartList}

% --Postconditions--
%
\begin{cpart}{Postconditions}
The geofence functionality is disabled in the server.
\end{cpart}

\clearpage
