\section{Geofence Settings: Enable/Disable}

% --Description--
%
\begin{cpart}{Description}
Because the geofence functionality will drain the battery quite a lot, it is important to let the user have the ability to disable and enable all of the functionalities whenever he or she wants.
\end{cpart}


% --Actors--
%
\begin{cpart}{Actors}
User
\end{cpart}

% --Preconditions--
%
\begin{cpartList}{Preconditions}
\item The smartphone application is in the foreground.
\item The user is logged in to his or her account.
\item The geofence functionality is \textbf{enabled}.
\end{cpartList}

% --Basic Flow--
%
\begin{cpartList}{Basic Flow}
  \item The user taps on the settings icon.
  \item The smartphone presents the user with the settings view.
  \item The user taps on the enable/disable switch, disabling the functionality.
  \item The smartphone application saves the setting.
  \item The smartphone disables the geofence functionality.
\end{cpartList}

% --Alternate Flows--
%
\begin{cpartList}{Alternate Flows}
  \begin{innerList}{5}{a}{The geofence functionality is already disabled.}
    \item The smartphone enables the geofence functionality.
  \end{innerList}
  \begin{innerList}{5}{b}{The geofence functionality is already disabled, and the GPS hardware is off.}
    \item The smartphone notifies the user that the GPS hardware, required for the geofence functionality to work, is disabled.
    \item The smartphone asks the user if he or she wants to enable the GPS hardware.
    \item The user agrees.
    \item The smartphone enables the GPS hardware.
    \item The smartphone enables the geofence functionality.
    \begin{innerList}{3}{a}{The user declines.}
      \item The use case is terminated.
    \end{innerList}
  \end{innerList}
\end{cpartList}

% --Postconditions--
%
\begin{cpart}{Postconditions}
All the geofence related functionality is disabled.
\end{cpart}

\clearpage
