\section{Geofence: Perimeter Breach}

\begin{cpart}{Description}
Geofence is the virtual perimeter for a real-world geographic area, according to Wikipedia. In this context, the geofence is the virtual perimeter for when the automatic turn-on feature will be triggered.
\end{cpart}

\begin{cpart}{Actors}
User
\end{cpart}

\begin{cpartList}{Preconditions}
\item The user has activated the geofence function in his or her smartphone.
\item The smartphone's GPS hardware is activated.
\item The application is running, either in foreground or background.
\item The user is logged in to the application.
\end{cpartList}

\begin{cpartList}{Basic Flow}
\item The user closes in to the virtual perimeter.
\item The smartphone detects the breach of the virtual perimeter.
\item The smartphone sends a request to the system to turn on the coffee machine.
\item The system sends a notification to the smartphone that the coffee machine has been turned on.
\item The system writes a log entry for the activity of the user with the current time and date.
\item The smartphone notifies the user that the coffee machine has been turned on.
\end{cpartList}

\begin{cpartList}{Alternative Flows}
\begin{innerList}{1}{a}{The user is already inside the geofence perimeter.}
\item The basic flow continues at step 3.
\end{innerList}
\begin{innerList}{4}{a}{The system sends a notification that the coffee machine already is on.}
\item The use case ends without any other action.
\end{innerList}
\begin{innerList}{4}{b}{The system sends a notification that the functionality is disabled in the server.}
\item The application notifies the user that the notification is disabled on the server.
\item The application turns the geofence functionality off inside the smartphone.
\end{innerList}
\end{cpartList}

\begin{cpart}{Postconditions}
The coffee machine is on.
\end{cpart}

\clearpage
