\section{User Login via Smartphone}

\begin{cpart}{Description}
When the user wishes to login via his or her smartphone. Very similar to the regular User Login use case.
\end{cpart}

\begin{cpart}{Actors}
User
\end{cpart}

\begin{cpartList}{Preconditions}
\item User's smartphone is on.
\item User's smartphone views the installed apps.
\end{cpartList}

\begin{cpartList}{Basic Flow}
\item The user taps on the icon that corresponds to the coffee machine application.
\item The system presents the user with the login page.
\item The user taps on the username text field.
\item The user types in his or her username.
\item The user taps on the password field.
\item The user types in his or her password.
\item The user taps the login button.
\item The system logs in the user.
\item The system makes an entry in the log file about the login from the smartphone.
\item The system presents the user with the default post-login page.
\end{cpartList}

\begin{cpartList}{Alternate Flows}
\begin{innerList}{5}{a}{The user taps on the "next field" key on the keyboard.}
\item The basic flow continues from step 6.
\end{innerList}
\begin{innerList}{7}{a}{The user taps the enter key on the keyboard.}
\item The basic flow continues from step 8.
\end{innerList}
\end{cpartList}

\begin{cpartList}{Exception Flows}
\begin{innerList}{8}{a}{The user has typed in a bad username or password.}
\item The system notifies the user that he or she is not logged in.
\end{innerList}
\begin{innerList}{8}{b}{The maximum number of bad tries has been reached.}
  \item The system notifies the user that the maximum number of bad tries has been reached.
  \item The system disables the user's account.
  \item The use case exits.
\end{innerList}
\end{cpartList}

\begin{cpart}{Postcondition}
User is logged in.
\end{cpart}
