\section{Password Recovery}

% --Description--
%
\begin{cpart}{Description}
The user has the option to recover his password during login in case he does not remember the password, which makes it impossible for him to login.
\end{cpart}


% --Actors--
%
\begin{cpart}{Actors}
User
\end{cpart}

% --Preconditions--
%
\begin{cpart}{Preconditions}
The application is started and the user is on the login page.
\end{cpart}

% --Basic Flow--
%
\begin{cpartList}{Basic Flow}
  \item The user requests password recovery.
  \item The system requests account data from the user.
  \item The user enters his username.
  \item The system verifies that the username exists.
  \item The system sends an email to registered mail address for the user with a link to a page which allows the user to choose a new password.
  \item The user follows the link and fills out the form.
  \item The user sends the form to the system.
  \item The system verifies that the new password fulfills the set criteria.
  \item The system updates the password of the user with the data from the form.
  \item The system writes a log entry for the activity of the user with the current time and date.
\end{cpartList}

% --Exception Flows--
%
\begin{cpartList}{Exception Flows}
  \begin{innerList}{4}{a}{The entered data does not exist.}
    \item The system shows an error message.
    \item The use case is exited.
  \end{innerList}
  \begin{innerList}{9}{a}{The entered password does not fulfill the criteria.}
    \item The system show an message that the password did not fulfill the criteria and reminds the user of what the criteria for passwords are.
  \end{innerList}
\end{cpartList}

% --Postconditions--
%
\begin{cpart}{Postconditions}
The user's password is updated.
\end{cpart}

\seq{passwordRecovery}
