\section{User Login}

\begin{cpart}{Description}
The users go through this use case whenever they want to access any of the user interfaces. After logging in the user should be redirected to the main page of the application.
\end{cpart}

\begin{cpart}{Actors}
User
\end{cpart}

\begin{cpart}{Preconditions}
The application is started
\end{cpart}

\begin{cpartList}{Basic Flow}
  \item The user types in the username and password.
  \item The system logs in the user.
  \item The system writes a log entry for the activity of the user with the current time and date.
  \item The system checks if a cookie exists for the user.
  \item The system asks if the user wants to store a cookie.
  \item The user accepts and a cookie is stored for further usage.
\end{cpartList}

\begin{cpartList}{Alternate Flows}
  \begin{innerList}{1}{a}{The user already has a cookie in store.}
    \item The system checks that the cookie is still valid.
    \item The system logs in the user automatically.
  \end{innerList}
  \begin{innerList}{5}{a}{The user declined the storage of a cookie.}
    \item The system does not store a cookie for further usage.
  \end{innerList}
\end{cpartList}

\begin{cpartList}{Exception Flows}
  \begin{innerList}{2}{a}{The entered username does not exist.}
    \item The system shows an error message.
    \item The use case is terminated.
  \end{innerList}
  \begin{innerList}{2}{b}{The entered password is incorrect.}
    \item The system shows an error message.
    \item The use case is terminated.
  \end{innerList}
  \begin{innerList}{2}{c}{The maximum number of wrong password entries has been reached.}
    \item The system shows an error message.
    \item The use case is terminated.
  \end{innerList}
  \begin{innerList}{4}{a}{The cookie is invalid or expired.}
    \item The system notifies the user that the cookie is invalid.
    \item The user is sent to the login page and needs to enter the username and password to continue.
  \end{innerList}
\end{cpartList}

\begin{cpart}{Postconditions}
The user is redirected to the correct page.
\end{cpart}

\seq{userLogin}
