\section{Introduction}

\subsection{Purpose}

The purpose of this document is to enunciate the functional and non-functional
requirements related to the system as a whole.


\subsection{Project Description}

Within the company \textit{Softwerk AB} a constant supply of coffee is needed to ensure maximal work efficiency. To be able to keep a steady flow of this liquid energy, a coffee machine control system will be created to manage the brewing of coffee remotely as well as manage interaction between the coffee machine and the user.


\subsection{Scope}

The scope of this document is kept within the frames of the requirements that concerns the system in one way or another. Real-world reqirements is kept at a minimum. All information and data is gathered from meetings with the customer, as well as a project description provided by the same.

\section{System-Wide Functional Requirements}

\begin{itemize}
\item Reporting: The status of the coffee machine must be given in a
human readable format.
\item Interacting: The system must provide means to interact with the
coffee machine in order to start and stop the machine.
\item Automatic Start: The system may start automatically if the user is
within a specified distance from the machine.
\item User Management: Users must have an account, and those accounts
must be managed by an administrator.
\item Statistics: Users must be able to, in a human readable format, view statistics of how often, by whom, and when the coffee machine is in use.
\item Manual Override: The system should be able to be manually overridden
to let the user circumvent the automatic system.
\end{itemize}

\section{System Qualities}

\subsection{Usability}

\begin{itemize}
\item Any employee of Softwerk AB must be able to operate the system, regardless of profession.
\item The statistics should be displayed in such a way that the customer finds it is easy to understand.
\end{itemize}

\subsection{Reliability}

\begin{itemize}
\item The system must accessible at all times.
\item After the startup of the hardware, the system must be ready to use without any user intervention.
\end{itemize}

\subsection{Performance}

\begin{itemize}
\item The system must be able to handle at least as many users at once as there are employees at Softwerk.
\item The startup time of the system should be less than two minutes.
\item Any request from the user should be completed within 10 seconds.
\end{itemize}

\subsection{Supportability}

\begin{itemize}
\item The system must be able to run on the Operating Systems that the company requests.
\item The system must be able to run on the Web Browsers that the company requests.
\end{itemize}



\section{System Interfaces}

\subsection{User Interfaces}

\begin{itemize}
\item The system should provide support for three different interfaces. All three interfaces should provide the same functionality.
  \begin{itemize}
  \item One web interface to use in browsers.
  \item One interface to use on Android 4.x smartphones.
  \item One interface to use on Android 5.x smartphones.
  \end{itemize}

\item The web interface should have a responsive design regarding CSS Media Queries.

\item The following elements should be graphically represented in the user interface:
  \begin{itemize}
  \item The statistics.
  \item The status of the coffee machine.
  \item Optionally also a video stream of the coffee machine.
  \end{itemize}
\end{itemize}

\subsection{Interfaces to External Systems or Devices}

\subsubsection{Hardware Interfaces}

\begin{itemize}
\item The system must have a semiconductor relay to switch the state of any hardware connected to it.
\item The system should have a phyiscal state-switch override button.
\end{itemize}

\subsubsection{Communications Interfaces}

\begin{itemize}
\item The system needs to be able to communicate with other systems either through a Local Area Network or trough a World Area Network.
\end{itemize}

\section{System Constraints}

\begin{itemize}
\item The system will be run on a Raspberry Pi Model B which has the following constraints:
  \begin{itemize}
  \item It is a ARM platform, meaning that the compiled software might not work on a x86 platform.
  \item It has 512mb of memory, which might have an impact on response times and overall stability of the system.
  \end{itemize}
  \end{itemize}

\section{System Documentation}

\begin{itemize}
\item The system should be delivered with a user manual which must fulfill the following requirements:
  \begin{itemize}
  \item All parts of the document must be written in such a way that the customer will be able to follow them.
  \item It must have a guide on how to install the system.
  \item It must have a instruction manual on how to operate the system.
  \end{itemize}
\end{itemize}
