\section{Introduction}

\subsection{Purpose}

The purpose of this document is to outline the vision for the system of the Coffee Machine and describe the high-level requirements. It will especially focus on the following:

\begin{itemize}

\item Identify the problems and constraints that the customer is experiencing with the current prototype of the product.
\item Collect and explain the customer’s demands and requests on the new system.
\item Introduce a solution.
\item Identify any issues or constraints with the solution.
\item Identify the stakeholders and users.
\item Present the product development team.

\end{itemize}

\subsection{Scope}

The Scope of this document is the Coffee Managment System for Softwerk AB. The System is in development by Team 5 and is developed for the ISEP project. The Information for this document was collected from the ISEP Introduction document and two meetings with the customer.

\clearpage

\section{Problem Statement}

\subsection{The problem of:}

\begin{itemize}
\item No user friendly way to remotely switch on/off the coffee machine.
\item Not being able to remotely see the current status of the coffee machine.
\item Not having any statistics on by who, when, and how often the coffee machine is used.
\end{itemize}

\subsection{Affects:}

\begin{itemize}
\item The employees of the company.
\item The coffee budget.
\item The overall productivity of the employees in the company.
\end{itemize}

\subsection{Causing the impact of:}

\begin{itemize}
\item An unreliable way to control the coffee maker.
\item An unnecessarily complicated way to control the coffee machine via SSH and VPN.
\item No one to be held responsible if the coffee machine is switched on/off when it is not supposed to.
\item No way to keep track of coffee expenses, as well as the overall coffee consumption in the company.
\end{itemize}

\subsection{A solution provides:}

\begin{itemize}
\item Comfortability and security, knowing that the coffee always will be ready when you arrive at the office.
\item An overall higher usability of the coffee machine.
\item A solid base to develop new features on top of.
\item Higher productivity with fewer and shorter interruptions throughout the day to check the state of the coffee machine.
\end{itemize}

\clearpage

\section{Product Features}

\subsection{Musts}

\textit{The solution must:}

\begin{itemize}
\item have a web-interface to control the coffee machine through the raspberry pi.
\item have a mobile friendly design.
\item have a user management system allowing for users to be created, updated, deleted and deactivated.
\item be able to view the current status of the coffee machine and change it.
\item provide secured login through the use of a SSL certificate.
\end{itemize}

\subsection{Shoulds}

\textit{The solution should:}

\begin{itemize}
\item provide protection from account hacking by locking any user account that gets accessed with incorrect data too many times.
\item provide a comfortable way to log in without having to enter login data.
\item be able to give information about every user of the program.
\item show statistics filtered by users and time frame.
\item keep track of statistics concerning coffee consumption.
\item have a status history to keep track of interactions.
\item have a visual representation of statistics in form of a pie chart and a histogram.
\end{itemize}

\clearpage

\subsection{Mays}

\textit{The solution may:}

\begin{itemize}
\item be ported to android.
\item enable automatic start when users approach.
\item display a video of the coffee machine for the user to see if the coffee is done.
\item be able to recognize if coffee is done by the use of image recognition.
\item have an exterior design, wooden with a big switch that changes the state of the coffee machine.
\item have a physical button that changes the state of the coffee machine.
\item have an indicator to show that the users needs to buy more coffee.
\end{itemize}

\section{Constraints}

\subsection{Design}

\begin{itemize}
\item The system must use a layered architecture. A server in the bottom, using an API, with an abstraction layer in the middle that communicates with the website on top.
\item The user interface must be responsive and modern.
\item The system should be based on the existing proof of concept prototype hardware, which is a Raspberry PI with a semiconductor relay connected to it.
\end{itemize}

\subsection{Time}

\begin{itemize}
\item The project must be done and all documentation must be handed in by the end of May.
\item The first working prototype must be presented on March 11 at the latest.
\end{itemize}

\subsection{Hardware}

\begin{itemize}
\item The system must use the provided hardware parts - a Raspberry PI, a semiconductor relay, and an extension cord.
\item The user hardware to access the coffee machine includes mobile devices running android, PC's (Linux, Windows), and Macs. %Not sure if they actually do use linux pcs and macs
\end{itemize}

\section{Risks}

\textit{Risks of the project include:}

\begin{itemize}

\item Insufficient knowledge of the technologies to be used (Raspberry Pi,
Android, ...).
\item Only part of the team has the Raspberry PI physically available.
\item Bad communication with the customer.
\item Not fully understanding the customer's requirements
\item Insufficient amount of testing due to the fact that only one part of the team has the Raspberry Pi.
\item More members drop out from the project, which could lead to a staff shortage.
\item Too short of a time budget which may cause an unfinished, or insufficiently developed product.
\end{itemize}

\clearpage

\section{Stakeholders and User Descriptions}

\subsection{Stakeholders}

\begin{itemize}
\item \textbf{Softwerk AB, Dr. Rüdiger Lincke}
\begin{itemize}
\item The client of the project.
\item Monitors the project.
\item Evaluates the solution quality and design.
\end{itemize}

\item \textbf{Softwerk AB, the employees}
\begin{itemize}
\item The users of the product.
\item Involved in the late testing part of the project.
\end{itemize}

\item \textbf{Team 5 at the ISEP project}
\begin{itemize}
\item Directly involved with the project.
\item Individually graded based on effort.
\item Individually graded based on the solution quality.
\end{itemize}

\item \textbf{Jesper Andersson, ISEP responsible}
\begin{itemize}
\item Monitors the project.
\item Evaluates the solution quality and design.
\item Sets the grades of the projects.
\end{itemize}
\item \textbf{Apostolos Ampatzoglou, ISEP responsible}
\begin{itemize}
\item Monitors the project.
\item Evaluates the solution quality and design.
\item Sets the grades of the projects.
\end{itemize}
\end{itemize}

\subsection{User Descriptions}
\begin{itemize}
\item \textbf{The employees of Softwerk AB.}
\begin{itemize}
\item The employees are experienced developers.
\item They have high expectations of the solution.

\end{itemize}
\end{itemize}

\clearpage

\section{Project Team Members}

\begin{table}[h]
\begin{tabular}{lll}
\textbf{Resource} & \textbf{Project Role} & \textbf{Area Represented} \\  \hline \\

Efrén Martin Garcia & Global Team Leader & Planning \\
Joost Ouwerling & Dutch Team Leader & Planning, Development \\ \\
\hdashline \\
Ted Sundström & Analysist (Lead) and Tester & Analysis and Testing\\ \\
\hdashline \\
Jose Jimenez	Hernandez & Designer (Lead) & Design \\
Robert Hallink & Designer & Design \\ \\
\hdashline \\
Julian Vos & Developer (Lead) & Development \\
Ronald Kruizinga & Developer & Development \\ \\
\hdashline \\
Florian Schiedt &Tester (Lead) and Analysist & Testing and Analysis

\end{tabular}
\end{table}
